---
name: Gerard
surname: Chung
position: "Assistant Professor"
address: "Social Work, National University of Singapore"
#phone: +1 22 3333 4444
www: gerardchung.com
email: gerard@nus.edu.sg
#twitter: "GerardChung"
github: gerardchung
researchgate: Gerard_Chung
linkedin: gerardchung
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv  # moderncv hyndman awesomecv
headcolor: 228b22   # https://www.colorhexa.com/     (228b22) (ff9900) (339900) (6699ff)
#bibliography: gerard.bib
#bibliography_published: "Published.bib"
#nocite: '@*' # don't change this if you want to print out all the refs

# this code belows is needed so that the xls tables will work for longtable = T
header-includes:
- \usepackage{longtable}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(readr)
library(knitr)
library(float)
library(kableExtra)
library(ggplot2)

options(encoding = "UTF-8")
#options(tinytex.verbose = TRUE)
options(knitr.kable.NA = '')
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)


```


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PHD SOCIAL WORK", "2021", "University of North Carolina at Chapel Hill", "USA",
  "Master of Social Work", "2016", "National University of Singapore", "Singapore",
  "Bachelor of Arts (Social Work)", "2007", "National University of Singapore", "Singapore",
  "Graduate Diploma in Solution-focused Brief Therapy", "2011", "Edith Cowan University", "Australia"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Work Experiences


```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '2023 - ongoing', "Assistant Professor, Social Work, NUS","Research, Teaching",
  '2022 - 2023', "Research Fellow, A*STAR, Singapore","Data Analysis, Research, Mentorship",
  '2021 - 2023', "Research Fellow, Social Service Research Centre, NUS","Research consultancy, Data analyst, Mentorship, Training",
  '2014 - 2017', "Research manager 'Strengthening Families Together Pilot', NUS","Project manager, Data manager, Data Analyst, Training",
  '2008 - 2013', "Senior Social Worker, Fei Yue Family Service Centre & Child Abuse Specialist Centre","Case management; Groupwork; Clinical supervision; Training",
  
  
  
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```




# Grants, Awards, Selections, and Fellowships

```{r}
tribble(
  ~Year, ~Name, ~Institution,
  2022, "Inaugural Summer Institutes of Computational Social Science in Singapore", "SICSS",
  2021, "Injury Violence & Prevention Fellowship (US$3,000)", "Injury Prevention Research Center, UNC",
  2021, "Ee Peng Liang Scholar", "Ee Peng Liang Memorial Fund, NUS",
  2020, "Injury Violence & Prevention Fellowship (US$3,000)", "Injury Prevention Research Center, UNC",
  2017, "Merit Assistantship (4 years funding)", "Graduate school, UNC",
  2014, "Alice Goh Scholarship", "NUS",
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution
  )

```



# Publications (First author) 

```{r pub}

pub <- read_csv("pub_published_table.csv", skip_empty_rows = TRUE)
pub <- pub %>%
  arrange(desc(year))
knitr::kable(pub, "latex", booktabs = TRUE,
             col.names = c("Authors", "Year", "Title", "Journal"),
             longtable = TRUE) %>%
  kableExtra::column_spec(1, width = "5cm") %>%
  kableExtra::column_spec(2, width = ".5cm") %>%
  kableExtra::column_spec(3, width = "7cm") %>%
  kableExtra::column_spec(4, width = "4cm") %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "repeat_header"),
                            font_size = 9)

```
\newpage
# Publications (Co-author) 

```{r coauthor}

pub <- read_csv("pub_coauthor_table.csv", skip_empty_rows = TRUE)
pub <- pub %>%
  arrange(desc(year))
knitr::kable(pub, "latex", booktabs = TRUE,
             col.names = c("Authors", "Year", "Title", "Journal"),
             longtable = TRUE) %>%
  kableExtra::column_spec(1, width = "5cm") %>%
  kableExtra::column_spec(2, width = ".5cm") %>%
  kableExtra::column_spec(3, width = "7cm") %>%
  kableExtra::column_spec(4, width = "4cm") %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "repeat_header"),
                            font_size = 9)

```
# Publications (In Review) 

```{r In review}

pub <- read_csv("pub_inreview_table.csv", skip_empty_rows = TRUE)
pub <- pub %>%
  arrange(desc(year))
knitr::kable(pub, "latex", booktabs = TRUE,
             col.names = c("Authors", "Year", "Title", "Journal"),
             longtable = TRUE) %>%
  kableExtra::column_spec(1, width = "5cm") %>%
  kableExtra::column_spec(2, width = ".5cm") %>%
  kableExtra::column_spec(3, width = "7cm") %>%
  kableExtra::column_spec(4, width = "4cm") %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "repeat_header"),
                            font_size = 9)

```



# Research Projects

## Ongoing Projects 

* In-Work Poverty and the Challenges of Getting By Among the Young
    - Co-PI/Social Science Thematic Research Grant (Type B)
    - Website: https://fass.nus.edu.sg/ssr/research-projects/in-work-poverty-challenges-getting-by-among-the-young/ 
 
<br>

* Building science and tech tools for text-based counseling
    - PI, in collaboration with Fei Yue, Seed Grant 
   
<br>

* DADSCAN (Dads Advancing Data for the development of Singaporean Children and Adolescents Now!)
  - Collaborator, A*STAR 
  - www.dadscan.org

## Summary of Research Projects

```{r researchprojects}

res_proj <- read_csv("research_proj.csv", skip_empty_rows = TRUE)
res_proj <- res_proj %>%
 # mutate(amount = scales::dollar(amount, prefix = "£")) %>%
  arrange(desc(year))
knitr::kable(res_proj, "latex", booktabs = TRUE,
             col.names = c("Funder", "Project", "Year", "Role"),
             longtable = TRUE) %>%
  kableExtra::column_spec(1, width = "2.0cm") %>%
  kableExtra::column_spec(2, width = "9cm") %>%
  kableExtra::column_spec(3, width = "1.5cm") %>%
  kableExtra::column_spec(4, width = "4cm") %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "repeat_header"),
                            font_size = 10)

```

# Presentations  

```{r}
library(dplyr)
bibliography_entries("presentations/presentations.bib") 

```

# News/Media   

```{r}
library(dplyr)
bibliography_entries("news_media/news_media.bib") 

```


# Reports/Articles  

```{r}
library(dplyr)
bibliography_entries("reports_articles/reports_articles.bib") 

```

# Teaching Experience

## Primary Instructor

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '06/2023 - 12/2023', "SW4103 Advanced Research & Evaluation (NUS)","Masters in SW class;Teaching", 
  '06/2023 - 12/2023', "SWM5117A Practive Research Capstone 1 (NUS)","Teaching; Mentoring", 
  '01/2023 - 04/2023', "Quantitative Research Methods (SSR)","Teaching", 
  '02/2022 - 04/2022', "Mentoring in Research Skills (SSR)","Small group mentoring; Teaching", 
  '01/2022 - 01/2022', "Research Skills for Social Service Professionals (SSR)","Course design; lectures", 
  '09/2014 - 09/2014', "Financial Cases: Assessment, case management, and intervention (Academy of Human Development Singapore)","Course design; lectures", 
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```
## Graduate Student Instructor

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '01/2021 - 05/2021', "SOWO 918 : Applied Regression Analysis and Generalized Linear Models", "Two Guest Lectures; Grading student essays; office hours; supervising student research projects",
  '08/2020 - 12/2020', "SOWO 911 :  Introduction to Social Statistics and Data Analysis","Lectures; Grading student essays & assignments; office hours; supervising student research projects",
  '08/2019 - 12/2019', "SOWO 911 :  Introduction to Social Statistics and Data Analysis","Grading student essays & assignments; office hours; supervising student research projects",
  '01/2019 - 05/2019', "SOWO 500: Human Development in Context I: Infancy to Adolescence","Two Lectures;  Grading assignments and exams; office hours",
  '01/2018 - 06/2018', "SOWO 800 : Evaluation of Social Work Intervention","Grading student essays; office hours; supervising student research projects"
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```

# Professional Service/Consultancy

## Research Consultancy/Collaborations

* Kampong Kapor FSC (2023)
    - Data curation and Dashboard 

<br>    

* Fei Yue Community Services (2021-2023)
    - Create SOP for Data Management and Quality for Research Team
    - NLP work on Adoption Assessment Reports
    
<br>
* Blended Concepts (2023)
    - Development of Logic Model 
* The Samaritans of Singapore SOS (2017-2018)
* Agency for Integrated Care AIC (2017-2018)


## Ad Hoc Reviewer

* Journal of Child & Family Studies
* Journal of Family Violence 
* Child & Family Social Work
* Family Relations
* Interpersona
* Current Psychology
* Infancy
* Canadian Journal of Community Mental Health
* Child & Youth Service Review
* Family Relations
* Asia Pacific Journal of Social Work
* British Journal of Psychology
* Scandinavian Journal of Psychology
* Journal of Family Issues


## Editorial

* Editorial assistant, Asia Pacific Journal of Social Work and Dev (2013-2017)


# Social Work Practice Experience


```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '09/2008 - 09/2013', "Senior Social Worker, Fei Yue Family Service Centre & Child Abuse Specialist Centre","Case management; Groupwork; Clinical supervision; Training"
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Duty
  )
```



# References

```{r}
tribble(
  ~Name, ~Title, ~Contact,
  'Mimi Chapman, Ph.D.',"Associate Dean for Doctoral Education; Frank A. Daniels Distinguished Professor for Human Service Policy Information, Chair of the UNC Chapel Hill Faculty, University of North Carolina at Chapel Hill", "mimi@email.unc.edu",
  'Chen Ding-Geng, Ph.D.',"Kuralt Distinguished Professor, School of Social Work; Professor in Biostatistics, Gillings School of Global Public Health, University of North Carolina at Chapel Hill", "dinchen@email.unc.edu",
  'David Ansong, Ph.D.',"Kuralt Early Career Distinguished Associate Professor; Faculty Fellow at Global Social Development Innovations, University of North Carolina at Chapel Hill", "ansong@email.unc.edu",
  'Paul Lanier, Ph.D.',"Kuralt Distinguished Associate Professor; Associate director, Jordan Institute of Families, University of North Carolina at Chapel Hill", "planier@email.unc.edu",

) %>% 
  detailed_entries(
    where = Contact,
    with = Name, 
    what = Title
  )


